---
title: "Assignment 1"
output:
  html_document:
    df_print: paged
---

# Loading Data into a Data Frame  

### Patrick Maloney, DATA607, Spring 2020

## Introduction
I chose to explore the data set about alcohol consumption from this fivethirtyeight article : https://fivethirtyeight.com/features/dear-mona-followup-where-do-people-drink-the-most-beer-wine-and-spirits/. Each row in the dataset repesents the average ammount of alcoholic beverages consumed per capita in a particular country in the year 2010.  
```{r}
library(devtools)
library(RCurl)
library(plyr)
```

## Load in the data set from GitHub

```{r}
x <- getURL("https://raw.githubusercontent.com/fivethirtyeight/data/master/alcohol-consumption/drinks.csv")
df <- data.frame(read.csv(text=x, header=T))
dim(df)
```
```{r}
head(df)
```


## In Which countries do people not drink alcohol?  

```{r}
abstain <- subset(df, total_litres_of_pure_alcohol == 0)
abstain
```

## Findings  

There are 13 countries where the average adult did not consume any alcohol in 2010.  The article starts off by listing a question from someone wondering how many people had never drank alcohol. My subset provides a quicker look at the countries where, on average, alcohol was not consumed in the year 2010, rather than having to dig through the entire table looking for zeros.


