---
title: "hw7"
author: "Patrick Maloney"
date: "3/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

For this assignment, I have created three files: one html, one xml, and one json.  I will explore the different processes for loading each into R.

## Libraries

These are the libraries that will be used

```{r}
library(RCurl)
library(jsonlite)
library(xml2)
library(rvest)
library(XML)
```

## HTML

This will use the 'rvest' library functions to find the html node "table" and then html_table to convert it to a dataframe.

```{r}
books_html <- read_html("https://raw.githubusercontent.com/pmalo46/DATA607/master/books.html")


df_html <- books_html %>%
                  html_node("table") %>%
                  html_table()

df_html
```

## XML

I will use the XML package to load the xml file into R.

```{r}
books_xml <- xmlInternalTreeParse(getURL("https://raw.githubusercontent.com/pmalo46/DATA607/master/books.xml"))
xml_apply <- xmlSApply(xmlRoot(books_xml), function(x) xmlSApply(x, xmlValue))
df_xml <- data.frame(t(xml_apply), row.names = NULL)
df_xml
```

## JSON

The JSON file will be imported into R very efficiently with the 'jsonlite' library.

```{r}
books_json <- fromJSON("https://raw.githubusercontent.com/pmalo46/DATA607/master/books.json") 
df_json <- as.data.frame(books_json)
df_json
```

## Conclusion

After importation, the HTML and XML tables looks the same, but the JSON table will require a little cleaning to fix the titles so that they match with the others.
