---
title: "Project 2a"
author: "Patrick Maloney"
date: "3/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Marriage Data Set

This data set contains information on the number of marriages per 1000 residents in different regions of the USA.

## Import data
```{r}
library(tidyr)
library(dplyr)
mar <- read.csv("https://query.data.world/s/zmajjvo77i3dfzcp5bdqxvbc2uw5h3", header=TRUE, stringsAsFactors=FALSE);
head(mar)
```

## Data Tidying
These wide data sets need to be pivoted to a long format.

```{r}
mar_long <- mar %>%
  pivot_longer(cols = 2:5, names_to = "Region", values_to = "Marriages")
head(mar_long, 25)
```

## Analysis

Have marriage rates increased or decreased overall?

```{r}
summary1 <- mar_long %>%
  group_by(year) %>%
  summarize(Region = "Total", Avg_Marriages = mean(Marriages, na.rm = TRUE))
summary1
```

It looks as tho marriage rates are decreasing. Let's confirm with a visual.
```{r}
x <- summary1$year
y <- summary1$Avg_Marriages
plot(x,y, type = 'l', xlab = 'Year', ylab = 'Marriages per 1k Residents')
```

Mariages have indeed sharply declined since 2000.
