---
title: "Project4"
author: "Patrick Maloney"
date: "4/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this project, a corpus of sample emails was created by downloading sample emails from Apache SpamAssassin, two sets of "spam" and "ham" (non-spam) emails were downloaded and unzipped. the files can be found at http://spamassassin.apache.org/old/publiccorpus/ for reproducibility, but I have already downloaded them locally. 
For those following along at home:
Training files:
20021010_easy_ham.tar.bz2
20030228_spam.tar.bz2

test files:
20030228_easy_ham_2.tar.bz2
20021010_spam.tar.bz2

### Import
```{r}
library(tm)
library(tidyverse)
library(stringr)
library(RTextTools)
```


Read in the files
```{r}
train_ham <- list.files("easy_ham/")
test_ham <- list.files("easy_ham_2/")
train_spam <- list.files("spam_2/")
test_spam <- list.files("spam/")

h_tr <- length(train_ham)
h_tst <- length(test_ham)
s_tr <- length(train_spam)
s_tst <- length(test_spam)

n <- h_tr + s_tr + h_tst + s_tst

emails <- rep(NA, n)

for(i in 1:h_tr){
  source <- str_c("easy_ham/", train_ham[i])
  y <- readLines(source)
  y <- str_c(y, collapse = "")
  emails[i] <- y
}

for(i in (h_tr + 1):(h_tr + s_tr)){
  x <- i - h_tr
  source <- str_c("spam_2/", train_spam[x])
  y <- readLines(source)
  y <- str_c(y, collapse = "")
  emails[i] <- y
}

for(i in (h_tr + s_tr + 1):(h_tr + s_tr + h_tst)){
  x <- i - (h_tr + s_tr)
  source <- str_c("easy_ham_2/", test_ham[x])
  y <- readLines(source)
  y <- str_c(y, collapse = "")
  emails[i] <- y
}

for(i in (h_tr + s_tr + h_tst + 1):n){
  x <- i - (h_tr + s_tr + h_tst)
  source <- str_c("spam/", test_spam[x])
  y <- readLines(source)
  y <- str_c(y, collapse = "")
  emails[i] <- y
}

```
### Build the Corpus
```{r}
corpus <- Corpus(VectorSource(emails))

control_list <- list(removePunctuation = TRUE, stopwords = TRUE,
                     removeNumbers = TRUE, tolower = TRUE, stemDocument = TRUE)

dtm <- DocumentTermMatrix(corpus, control = control_list)
dtm <- removeSparseTerms(dtm, 0.90)

spam <- c(rep("ham", h_tr),
          rep("spam", s_tr),
          rep("ham", h_tst),
          rep("spam", s_tst))
```
### Train the model
```{r}
n <- length(spam)
container <- create_container(dtm, labels = spam,
                              trainSize = 1:(h_tr + s_tr),
                              testSize = (h_tst + s_tst + 1):n,
                              virgin = FALSE)


model <- train_model(container, "TREE")
result <- classify_model(container, model)
show <- result %>%
  count(TREE_LABEL)
show
```



